---
title: "Cost-Benefit Analysis of Transitioning from Traditional Instructor-Led Training
  to Computer-Based Training"
author: "Your Name"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: true
    toc_depth: 2
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
---
\
\

# 1. Overview

This document outlines the cost-benefit analysis involved in transitioning select training modules from traditional Instructor-Led Training (ILT) to Computer-Based Training (CBT). It aims to identify the redevelopment costs, calculate the operational savings, and determine the break-even point, while also considering the effect on learning quality and participant experience.


# 2. Methodology

The analysis comprises three primary sections: determining the costs associated with redeveloping CBTs, estimating the operational savings gained by switching to CBTs, and evaluating the impact on learning quality and experience.


## 2.1. Redevelopment Costs

### 2.1.1. Definition of Variables

-   **Trainer Cost per Hour (TCH):** The hourly rate for trainers involved in redevelopment, which is constant across all modules.
-   **Number of Hours to Redevelop (NHR):** The estimated number of hours required to convert *i<sup>th</sup>* ILT modules into CBTs.  

The total redevelopment cost (TRC) is calculated as:

$$
TRC = \sum_{i=1}^{n} NHR_i TCH   
$$
```{r setup, include=FALSE}
# Define the redevelopment hours for each module and trainer's rate
redevelopment_hours <- c(3, 4, 1, 2)
trainer_rate <- 26
```

## 2.2 Savings from Transitioning to CBTs

### 2.2.1. Definition of Variables

-   **Number of ILT Modules Converted (NMC):** The total number of ILT modules transitioning to CBTs.
-   **Hours per ILT Module for the i<sup>th</sup> module (HM<sub>i</sub>):** The duration required to deliver the i<sup>th</sup> ILT module.
-   **Total Cost per Hour (TCH):** The hourly rate for trainers involved in redevelopment, which is constant across all modules.
The total savings (TS) considering each module's specific hours and cost savings is calculated as:

$$
TS = \sum_{i=1}^{NMC} HM_iTCH
$$
```{r include=FALSE}
# Calculate TRC and TS as before
TRC <- sum(redevelopment_hours * trainer_rate)
hours_saved_per_module <- rep(1, 4) # assuming 1 hour saved per module
TS <- sum(hours_saved_per_module * trainer_rate)

# Number of CBT sessions to project
num_sessions <- 10

# Calculate cumulative savings for each session
cumulative_savings <- cumsum(rep(TS, num_sessions))
```



## 2.3 Break-Even Point Calculation
The break-even point calculation (BEC) is the total redevelopment cost divided by the total savings, which is calculated as:

$$
BEC = \frac{TRC}{TS}
$$
This indicates the number of courses that need to be delivered in the CBT format to recover the redevelopment cost.

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Create a data frame for plotting
cbt_data <- data.frame(
  Session = 1:num_sessions,
  CumulativeSavings = cumulative_savings,
  RedevelopmentCost = TRC
)

# Create the break-even plot
library(ggplot2)
break_even_plot <- ggplot(cbt_data, aes(x = Session)) +
  geom_line(aes(y = CumulativeSavings), color = "blue", size = 1) +
  geom_hline(aes(yintercept = RedevelopmentCost), color = "red", linetype = "dashed", size = 1) +
  labs(
    title = "CBT Break-Even Analysis",
    x = "Number of CBT Sessions",
    y = "Cumulative Savings ($)",
    caption = "The dashed line represents the total redevelopment cost."
  ) +
  theme_bw () +
  geom_point(aes(y = RedevelopmentCost), color = "red") +
  geom_text(aes(x = 3, y = RedevelopmentCost, label = "Redevelopment Cost", vjust = -1))

# Display the plot
print(break_even_plot)
```
The chart demonstrates that the break-even point is reached after the third CBT session.From there, the cumulative savings continue to increase exponentially as more CBT sessions are delivered.

# 3. Impact on Learning Quality and Experience
Qualitative feedback will be gathered post-training via a survey to assess the impact on learning quality and experience. The survey will be administered to the participants of the CBTs and the results will be analyzed and a comparison analysis conducted with previous ILT-based survey data to determine the impact on learning quality and experience.